Penalized linear mixed models for structured genetic data

### 2021-03-05 main.tex
Section 6

\anna{The results of a genome-wide analysis of Empirical data agree with the findings of our simulation experiments, in particular that PC-lasso and LMM-lasso are able to substantially reduce selection bias compared to the ordinary lasso. Although PC-lasso was found to outperform LMM-lasso in terms of precision and estimation accuracy in this analysis, because the Empirical data consists of three distinct racial groups, its RRM (Supplementary Figure~\ref{fig:empirical}) demonstrates predominantly coarse population structure. Given our results in Section~\ref{sec:sim-fine-coarse}, we would expect LMM-lasso to outperform PC-lasso in the analysis of more finely structured genome-wide data.}

>>>>

\anna{The results of a genome-wide analysis of Empirical data agree with the findings of our simulation experiments, in particular that PC-lasso and LMM-lasso are able to substantially reduce selection bias compared to the ordinary lasso. We note that because the Empirical data consists of three distinct racial groups, its RRM (Supplementary Figure~\ref{fig:empirical}) demonstrates predominantly coarse population structure. Given our results in Section~\ref{sec:sim-fine-coarse}, we would expect LMM-lasso to perform even better in the analysis of more finely structured genome-wide data.}
